An Object-Logic Explanation for the Inconsistency in G\"odel's Ontological Theory

### 2016-07-10 Papers/2016/KI/main.tex
Simplify abstract
Remove duplicate paragraph

\begin{abstract}
  This paper discusses the discovery of the 
  inconsistency in G\"odel's
  ontological argument as a success story for artificial
  intelligence. Despite the popularity of G\"odel's argument, this
  inconsistency remained unnoticed until 2013, 
  when it was detected automatically by the 
  higher-order theorem prover \textsc{Leo-II} \cite{ECAI2014}. Complementing the meta-logic explanation for the inconsistency available in our IJCAI 2016 paper \cite{C55}, we present here a new purely object-logic explanation that does not rely on semantic argumentation.

@@

Interestingly, the refutation automatically generated by
\textsc{Leo-II} uses a symmetric accessibility relation, and thus
requires the modal logic \KB. The informal, human-constructed
refutation described above, on the other hand, requires only the
weaker modal logic \K. In our experiments \textsc{Leo-II} (like all
other HOL provers) was still too weak to automatically prove the
inconsistency already in logic \K. Hence, this remains an open problem for automated
theorem provers.

>>>>

\begin{abstract}
  This paper discusses the 
  inconsistency in G\"odel's
  ontological argument. Despite the popularity of G\"odel's argument, this
  inconsistency remained unnoticed until 2013, 
  when it was detected automatically by the 
  higher-order theorem prover \textsc{Leo-II} \cite{ECAI2014}. Complementing the meta-logic explanation for the inconsistency available in our IJCAI 2016 paper \cite{C55}, we present here a new purely object-logic explanation that does not rely on semantic argumentation.

@@
